\documentclass[10pt,a4paper]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage{fontspec}
\setmainfont{Poppins}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{graphicx}

% Page setup
\geometry{
    a4paper,
    left=0.75in,
    right=0.75in,
    top=0.6in,
    bottom=0.6in
}

% Colors
\definecolor{headerred}{RGB}{231, 76, 60}
\definecolor{darkgray}{RGB}{64, 64, 64}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=black,
    pdftitle={Abdallah Abedraba - Resume},
    pdfauthor={Abdallah Abedraba}
}

% Section formatting
\titleformat{\section}
    {\color{headerred}\large\bfseries\uppercase}
    {}
    {0em}
    {}
    [\titlerule]

\titlespacing*{\section}{0pt}{14pt}{8pt}

% Custom commands
\newcommand{\resumeSubheading}[4]{
    \vspace{4pt}
    \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
        \textbf{#1} & #2 \\
        #3 & #4
    \end{tabular*}
    \vspace{-4pt}
}

% Adjust list spacing
\setlist[itemize]{label=\scalebox{0.7}{$\bullet$}, leftmargin=*, itemsep=2pt, font=\small}

% Line spacing
\linespread{1.05}

% Remove paragraph indentation
\setlength{\parindent}{0pt}

% Remove page numbers
\pagestyle{empty}

\begin{document}

% Header
{\Huge \textbf{\color{headerred}Abdallah Abedraba}}

\vspace{8pt}

Seville • +34611159343 • \href{mailto:a@abedraba.com}{a@abedraba.com} • \href{https://linkedin.com/in/aabedraba}{linkedin.com/in/aabedraba}

\vspace{10pt}

% Summary
Software engineer with 8+ years building production systems at scale (200k+ users). Experience spanning IC roles to leading 10-person teams. Proven track record in developer tools, API infrastructure, and open-source projects.

\vspace{8pt}

\textbf{Skills:} Docker, GCP/AWS, Kubernetes, Serverless, GraphQL/REST, Next.js, Node, PostgreSQL, React, TypeScript

\section{Work Experience}

\resumeSubheading
{Producta.ai}{06/2024 - 11/2025}
{CTO, Co-Founder}{Seville, Spain (Remote)}

\begin{itemize}
    \item Built AI coding agent with novel multi-agent architecture replacing RAG with file summarization and layered code search; improved PR success rate from 50\% to 80\%.
    \item Architected agentic pipeline: input validation layer, multi-stage code search, expert model routing for complex tasks, and automated PR generation with GitHub integration.
    \item Designed zero-dashboard product living entirely in Linear/GitHub; reached ProductHunt \#3 and engaged 1000+ companies before pivoting based on market feedback.
\end{itemize}

\resumeSubheading
{Zuplo}{05/2023 - 06/2024}
{Staff Developer Relations}{Dubai, UAE (Remote)}

\begin{itemize}
    \item Built open-source Rate-My-OpenAPI tool (400 stars, +10k reports generated).
    \item Led Supabase integration building API key auth, rate limiting, and documentation features; resulted in 2x paid registrations.
    \item Led Go-To-Market strategy including conferences, partnerships, paid ads, and technical content.
\end{itemize}

\resumeSubheading
{Kubeshop}{11/2021 - 05/2023}
{Product Leader}{Dubai, UAE (Remote)}

\begin{itemize}
    \item I led engineering (10 reports), technical roadmap and architecture discussions, building open-source dev-tools like Testkube (Kubernetes test runner) and Kusk (API Gateway).
    \item Built serverless API gateway, matching Kusk feature parity in 1 month solo (vs. 8 months, 4-engineer team); extensive research into V8 isolates and edge architectures.
\end{itemize}

\resumeSubheading
{GreenMobility}{10/2019 - 11/2021}
{Fullstack Developer}{Copenhagen, Denmark}

\begin{itemize}
    \item I architected and built our platform from the ground up, delivering 2 consumer applications and scaling high-throughput systems (2M events per day) on serverless infrastructure.
    \item Shipped features daily to 200k customers and built internal portals to manage fleet of 600 cars.
\end{itemize}

\resumeSubheading
{Google}{09/2018 - 10/2019}
{Developer Relations}{Madrid, Spain}

\begin{itemize}
    \item Led training in European universities with 800 students, giving workshops on Google Cloud.
    \item Managed relationships with 65 developer communities in Europe with thousands of members, with 1-on-1 meetings to discuss needs and funding; and helped to create 15 new communities.
\end{itemize}

\section{Education}

\textbf{BS Computer Science} \\
Universidad de Jaen \hfill 09/2015 - 07/2018

\end{document}